---
title: "Coursera Statistical Inference Class"
author: "Pavel Gein"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
---

```{r echo = FALSE}
lambda <- 0.2
num.in.each <- 40
total.num <- 10000
```

Generate a exponential distributed numbers (with parametr lambda equals to `lambda`. We will generate a `total.num` rows, each consist of `num.is.each` numbers. Then we calculate their means (by row), and do our analysis.

```{r echo = TRUE}

data <- matrix(rexp(total.num * num.in.each, lambda), nrow = total.num, 
               byrow = TRUE)
means <- rowMeans(data)

make_plots <- function (data){
    par(mfrow = c(2, 1))
    hist(data)
    abline(v = 1 / lambda, lwd = 3, col = "red")
    dty <- density(data)
    plot(dty$x, dty$y, xlab = "", 
         ylab = "density", 
         xlim = c(2, 8),
         ylim = c(0, 1),
         type = "n")
    title(paste("sample mean of", total.num, "obs"))
    lines(seq(2, 8, length = 100), 
          dnorm(seq(2, 8, length = 100), mean =  1 / lambda, 
                sd = 1 / lambda / lambda / num.in.each), 
          col = "green", lwd = 3)
  lines(dty$x, dty$y, lwd = 2)
  abline(v = 1 / lambda, lwd = 3, col = "red")  
}
```


A variance of this data is `r var(means)`, but the theory says, that the variance should be `r 1 / lambda / lambda / num.in.each `

There is a histogrm of means and dencity plot:
```{r, echo = TRUE, fig.width=7.5, fig.height = 6}
   make_plots(means)
```
Red lines show a theoretical center and a green curve is normal distribution curve for a mean is equal to `r 1 / lambda` and a standart deviation is equal to `r 1 / lambda / lambda / num.in.each`


Estimate a coverage interval:
```{r echo = TRUE}
    mean(means) + c(-1, 1) * qnorm(0.975) * sd(means)/sqrt(length(means))
```

You can find a Rmd file [here](https://github.com/pavelgein/stat_infer)

