---
title: "Coursera Statistical Inference Class"
author: "Pavel Gein"
output:
  pdf_document:
    fig_caption: no
    keep_tex: yes
---

```{r echo = FALSE}
data(ToothGrowth)
library(ggplot2)
```

Load the data and look in summury of it
```{r echo = FALSE}
    summary(ToothGrowth)
```
We can see that there is only `r length(unique(ToothGrowth$dose))` different doses and only `r length(unique(ToothGrowth$supp))` different supps.

Divide dataset into groups by dose and supp and calculate mean. Make a plot with different colors for each supp:

```{r echo = FALSE}
    data <- aggregate(len ~ supp + dose, data = ToothGrowth, FUN = mean)
    ggplot(data, aes(x = dose, y = len, color = supp)) + geom_point() 
```

Investigate each group made by supp and dose (we've seen before a mean value of length).

```{r echo = FALSE}
    g <- ggplot(ToothGrowth, aes(x = len))
    #g  + facet_grid(supp ~ dose) + geom_line()
    ggplot(ToothGrowth, aes(x = len)) + geom_histogram(binwidth = 1) + facet_grid(supp ~ dose)
```

Investigate is there a difference beetwen mean value in each subgroup. We will use a T-test for this purpose. We assume that people doesn't change a dose and a supp and assume that people were chosen true randomly.

```{r echo = FALSE}
    un_dose <- unique(ToothGrowth$dose)
    un_supp <- unique(ToothGrowth$supp)
    for (dose in un_dose) {
        print(paste("T-test for ", dose, " dose:", sep = ""))
        data <- ToothGrowth[ToothGrowth$dose == dose, ]
        print(t.test(len ~ supp, data = data, var.equal = FALSE, paired = FALSE))
    }

```

We can conclude that there is a difference beetwen different supps.

You can find a Rmd file [here](https://github.com/pavelgein/stat_infer)

